Escape Analysis and Specialization in a Tracing JIT

### 2010-09-26 talk/pepm2011/paper.tex
fix an XXX, add a thought

Boxing of primitive types means that dynamic languages need to be able to handle
all objects, even integers, floats, bools etc. in the same way as user-defined
instances. Thus those primitive types are usually \emph{boxed}, i.e. a small
heap-structure is allocated for them, that contains the actual value. Boxing
primitive types can be very costly, because XXX

@@

>>>>

Boxing of primitive types means that dynamic languages need to be able to handle
all objects, even integers, floats, bools etc. in the same way as user-defined
instances. Thus those primitive types are usually \emph{boxed}, i.e. a small
heap-structure is allocated for them, that contains the actual value. Boxing
primitive types can be very costly, because a lot of common operations,
particularly all arithmetic operations, have to produce a new box, in addition
to the actual computation they do. Because the boxes are allocated on the heap,
producing a lot of them puts pressure on the garbage collector.

@@

XXX optimization particularly effective for chains of operations
